Item Construction Rules Revisited: Learnings from Measurement of Latent Variables with Gold Standard Items

### 2025-06-30 manuscript.qmd
remove redundant loadings from text

For body height, we obtained overall lower item loadings on the latent variable but high correlations with the gold-standard item of physical body height. In particular, the third item ("Chairs and tables are usually too low for me.") exhibited the highest loadings on the latent variable (two response categories: `r results$load_df_bifac |> filter(categories == 2, lhs == "height", rhs == "KGr_15") |> pull(est.std) |> printnum(gt = FALSE)`, and six response categories: `r results$load_df_bifac |> filter(categories == 6, lhs == "height", rhs == "KGr_15") |> pull(est.std) |> printnum(gt = FALSE)`). In contrast, item 11 ("I have to stand at the front of group photos so that I can be seen clearly.") and item 12 ("When I hug other people in greeting, I have to bend downwards.") were explained best by the self-reported physical body height independently of the response format.[^loadingsgreaterone] This pattern does not convincingly confirm the existence of a psychological latent variable after controlling for the self-reported physical measure and gender.

>>>>

For body height, we obtained overall lower item loadings on the latent variable but high correlations with the gold-standard item of physical body height. In particular, the third item ("Chairs and tables are usually too low for me.") exhibited the highest loadings on the latent variable for both response formats. In contrast, item 11 ("I have to stand at the front of group photos so that I can be seen clearly.") and item 12 ("When I hug other people in greeting, I have to bend downwards.") were explained best by the self-reported physical body height independently of the response format.[^loadingsgreaterone] This pattern does not convincingly confirm the existence of a psychological latent variable after controlling for the self-reported physical measure and gender.
